Outline--Draft JCP format for: Reactive Force Field for Perovskite--Based Solid Oxides and Its Application to Solid Oxide Electrolysis Cells

### 2019-05-17 Paper/paper.tex
Update paper.tex
After updating introduction, commented references that I may end up not using.

CO$_2$, electrocatalysts, and solid oxide fuels.\cite{
habisreutinger_photocatalytic_2013,
e.benson_electrocatalytic_2009,
pradeepindrakanti_photoinduced_2009,
indrakanti_quantum_2009,
zeng_review_2018,
yamada_systematic_2018,
kar_enhanced_2016,
grimaud_double_2013,
ni_electrochemical_2012,
tan_co_2011,
baniecki_photoemission_2008,
jia_heterogeneous_2017,
yin_oxide_2018,
zheng_review_2017,
andersson_review_2010,
beatriz_microwave-assisted_2015}

DFT studies.\cite{tian_dft_2018,
mayeshiba_strain_2017,
wang_oxidation_2006,
li_density_2013,
liu_influence_2018,
seo_design_2015,
evarestov_adsorption_2007,
pilania_establishing_2012,
pilania_adsorption_2010,
zurek_predicting_2015}

Molecular dynamics studies.\cite{wang_coarse-grained_2014}

>>>>

%CO$_2$, electrocatalysts, and solid oxide fuels.\cite{
%habisreutinger_photocatalytic_2013,
%e.benson_electrocatalytic_2009,
%pradeepindrakanti_photoinduced_2009,
%indrakanti_quantum_2009,
%zeng_review_2018,
%yamada_systematic_2018,
%kar_enhanced_2016,
%grimaud_double_2013,
%ni_electrochemical_2012,
%tan_co_2011,
%baniecki_photoemission_2008,
%jia_heterogeneous_2017,
%yin_oxide_2018,
%zheng_review_2017,
%andersson_review_2010,
%beatriz_microwave-assisted_2015}
%
%DFT studies.\cite{tian_dft_2018,
%mayeshiba_strain_2017,
%wang_oxidation_2006,
%li_density_2013,
%liu_influence_2018,
%seo_design_2015,
%evarestov_adsorption_2007,
%pilania_establishing_2012,
%pilania_adsorption_2010,
%zurek_predicting_2015}
%
%Molecular dynamics studies.\cite{wang_coarse-grained_2014}
